---
title: 'RLAB #2 Grandfather clocks'
author: "LCP"
date: "2/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA)
setwd("c:/data/csv")
clocks <-read.csv("clocks.csv", header=TRUE)
```

A Collector of antique grandfather clocks sold at auction believes that the price received for the clocks depends on both the age of the clocks (x1) and the number of bidders at the auction (x2). 



```{r meanprice, include=FALSE}
#Mean for the CV
#This output won't show up in the html file because Include=FALSE
y_bar <- mean(clocks$PRICE)
y_bar
```



```{r model1, echo=FALSE, include=TRUE}
model1 <-lm(PRICE~AGE, data=clocks)
summary(model1)
```

This text should include the linear regression equation, and your model utility checks for model #1.


```{r model2, echo=FALSE, include=TRUE}
model2 <-lm(PRICE~NUMBIDS, data=clocks)
summary(model2)
```

This text should include the linear regression equation, and your model utility checks for model #2.


Choose the model that's better and write about it here.
```{r predictions, echo=FALSE}
#Predicted 95% Confidence intervals for mean and individual values

newdata <-data.frame(AGE=160,NUMBIDS=11)

#STOP
#Son't run the code below until you choose your model
#Make sure you enter your choden model in place of ???

fitpredicted<-predict(model1,newdata, level=.95,interval="prediction")
fitpredicted
fitmean<-predict(model1,newdata, level=.95, interval="confidence")
fitmean
```
Using model #??, the predicted value of a clock that is 160 years old and is bid on by 11 bidders is ...

95% confidence interval
95% prediction interval


```{r scatterplots, fig.height=4, fig.width=6, echo=FALSE}
#Scatteplots for each predictor vs. price
plot(clocks$AGE, clocks$PRICE, xlab="Age", ylab="Price")
abline(lm(PRICE~AGE, data=clocks), col="red")
plot(clocks$NUMBIDS, clocks$PRICE, xlab="Number of Bidders", ylab="Price")
abline(lm(PRICE~NUMBIDS, data=clocks), col="green")
```

