---
title: "Stability (STB1 data)"
author: "LCP"
date: "2/12/2020"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = FALSE)

library(car)
setwd("c:/data/csv")
koleva <-read.csv("stb1.csv", header=TRUE)
options(scipen=5)
head(koleva)
bbatch <-as.character(koleva$Batch)
```



```{r slopes, include=TRUE, echo=TRUE}

model1 <-lm(Potency~Month+bbatch+Month*bbatch, data=koleva)
summary(model1)

anovatable1<-anova(model1)
anovatable1

pval1<-anovatable1$`Pr(>F)`[3]
pval1
```

For the interaction term, the p-value is `r pval1`. Compare this p-value (p1) to alpha=.25. If p1 is greater than .25, then the degradation rates are similar for the batches (parallel lines). The interaction term can be removed from the model, and the reduced model should be evaluated.

If the p-value is less than alpha=.25, then the slopes are different. The interaction model is used to predict the shelf-life. 

$~$

The interaction model is y=`r model1$coefficients[1]` + `r model1$coefficients[2]` 
* Month + `r model1$coefficients[3]` * batch2 + `r model1$coefficients[4]`* batch3 + `r model1$coefficients[5]`* Month * batch2 + `r model1$coefficients[6]`* Month * batch3

```{r y_intercepts}
model2 <-lm(Potency~bbatch+Month, data=koleva)
summary(model2)
anova(model2)

anovatable2<-anova(model2)
pval2<-anovatable2$`Pr(>F)`[2]
pval2
```


For the batch term, the p-value is `r pval2`. Compare this p-value (p2) to alpha=.25. If p1 is greater than .25, then the initial potency values of the batches are similar. The batch term can be removed from the model, and the reduced model should be evaluated.

If the p-value is less than alpha=.25, then the y-intercepts are different. The batch+Month model is used to predict the shelf-life. 

$~$

The batch+Month model is y=`r model2$coefficients[1]` + `r model2$coefficients[2]` 
* batch2 + `r model2$coefficients[3]` * batch3 + `r model2$coefficients[4]`* Month

```{r time_only}
model3 <-lm(Potency~Month, data=koleva)
summary(model3)
anova(model3)

anovatable3<-anova(model3)
pval3<-anovatable3$`Pr(>F)`[1]
pval3
```

If both the interaction term (i.e. degradation rate) and the batch term (i.e. the batch-to-batch variation at time t=0) are not significant at the alpha =. 25 level, then then the batches can be pooled. The simplest model, potency=time, is used to calculate the shelf life. 

$~$

The Month-only model is y=`r model3$coefficients[1]` + `r model3$coefficients[2]` * Month. 
